Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-19 paper.tex
update

\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of between two concepts related to outputs and inputs of two difference web services, and this matchmaking type is determined by the logic described in the $O$.

If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned.
If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned. 
If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned. 
If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b) \neq subsumes \mid fail$. The operator ``$ \rightarrow$'' means $a$ is passed to $b$. The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation as $b$ is fully satisfied by $a$.

@@

$E = \{e_{1}, e_{2},... e_{n} \}$ is a set of edges. where $e = O_{S_{m}} \cup I_{S_{n}} \cup $ $fullmatch(O_{m} \rightarrow I_{n})$ is source service $S_m$ and target service $s_n$

\subsection{Semantic Web Service matchmaking Type}\label{semantic Web service Discovery}

>>>>

\textbf{Definition 3.} Given $a, b \in C$, $type(a, b)$ returns the matchmaking types of two concepts, and this matchmaking type is determined by the logic described in the $O$. If both $a$ and $b$ are equivalent, $exact$ type ($a \equiv b$) is returned. If the concept of $a$ is a sub-concept of the concept of $b$ type ($a \sqsubseteq b$) is returned. If the concept of $a$ is a super-concept of the concept of $b$, $subsumes$ type ($a \sqsupseteq b$) is returned. If none of previous matchmaking types are returned, $fail$ type ($a \perp b$) is returned.

We use the $type(a, b)$ to define full matchmaking between two concept-related input and output of two services.

\textbf{Definition 4.} Given $(a \in O^{C}_{S_m}) \vee (b \in I^{C}_{S_n}) \wedge (m \neq n) $, a $full match(a \rightarrow b)$ holds if $type(a, b)$ returns $exact$ or $plugin$. The operator ``$ \rightarrow$'' means $a$ is passed to $b$, and $b$ is fully satisfied by $a$. The full match is a guarantee of completely valid  ``$ \rightarrow$'' operation, whereas, partial matches are not considered in this paper.

@@

$E = \{e_{1}, e_{2},... e_{n} \}$ is a set of edges, where each edge has a set of incoming outputs $O_{S_{src}}$ from source service $S_{src}$ and a set of outgoing inputs $I_{S_{src}}$ from target service $S_{tar}$.

$e = \{ (O_{S_{src}} \cup I_{S_{src}}) \mid \forall o \in O_{S_{src}}, \exists i \in O_{S_{src}} \wedge fullmatch (o \rightarrow i) \}$

\textbf{QoS Model in Weighted DAG}
